Quantifying sablefish movement in the northeast Pacific

### 2024-01-22 ms/manuscript.tex
git subrepo pull ms
subrepo:
  subdir:   "ms"
  merged:   "55f9e10"
upstream:
  origin:   "https://git.overleaf.com/5eb078b74a86f80001efc257"
  branch:   "master"
  commit:   "55f9e10"
git-subrepo:
  version:  "0.4.3"
  origin:   "https://github.com/ingydotnet/git-subrepo"
  commit:   "2f68596"
updated with ms and refs

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{bm}
\usepackage{lineno}
\renewcommand\linenumberfont{\normalfont\bfseries\small\color{darkgrey}}
\usepackage{booktabs}
\usepackage[round]{natbib}
\bibliographystyle{plainnat}
\usepackage{authblk}
% Linux Libertine:
\usepackage{textcomp}
\usepackage[sb]{libertine}
\usepackage[varqu,varl]{inconsolata}% sans serif typewriter
\usepackage[libertine,bigdelims,vvarbb]{newtxmath} % bb from STIX
\usepackage[cal=boondoxo]{mathalfa} % mathcal
\useosf % osf for text, not math
\usepackage[supstfm=libertinesups,%
  supscaled=1.2,%
  raised=-.13em]{superiors}
\usepackage{setspace}
\usepackage{siunitx}
\usepackage[section]{placeins} % Keep floats (figs, tabs, eqns) in the right section
% I assume these all work together to make nice colour
\usepackage[dvipsnames]{xcolor}
\definecolor{niceblue}{HTML}{236899} % Depends \usepackage[dvipsnames]{xcolor}
\definecolor{darkgrey}{HTML}{A9A9A9} % Depends \usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=niceblue,
    citecolor=niceblue,
    linkbordercolor = white
}
% End nice colour
\usepackage{pgfplotstable} % For tables
\pgfplotsset{compat=1.16} % For tables
\input{./values/values}
\usepackage{graphicx}
\graphicspath{ {./figs/} }
\newcommand{\lr}[1]{{\color{blue}#1}}
% \newcommand{\bc}[1]{{\color{red}#1}}

\title{Quantifying sablefish movement in the northeast Pacific}
% Tag movement reveals transboundary sablefish stock structure in the northeast Pacific
% Movement ecology and transboundary stock structure of sablefish in the northeast Pacific

\author[1]{Luke A. Rogers}
\author[]{...}
% \author[2]{Brendan Connors}
% \author[1]{Sean C. Anderson}
% \author[3]{Melissa Haltuch}
% \author[4]{Maia Kapur}
% \author[5]{Dana Hanselman}
% \author[5]{Kari Fenske}
% 
\affil[1]{Pacific Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, V9T 6N7, Canada}
% \affil[2]{Institute of Ocean Sciences, Fisheries and Oceans Canada, Sidney, BC, V8L 5T5, Canada}
% \affil[3]{Northwest Fisheries Science Center, National Oceanic and Atmospheric Administration, Seattle, WA 98112, USA}
% \affil[4]{School of Aquatic and Fisheries Sciences, University of Washington, Seattle WA 98105, USA}
% \affil[5]{Alaska Fisheries Science Center, National Oceanic and Atmospheric Administration, Juneau, AK 99801, USA}

@@

\maketitle
\linenumbers
\setcounter{secnumdepth}{0} % Removes section numbers

\section{Overview}
\subsection{One single eight-region spatial scale}
Animal movement rates underlie spatial population dynamics and can influence the effectiveness of management strategies for harvested species. We quantified sablefish movement rates among geographic regions in the northeast Pacific by fitting Markov movement models to forty years of tag--recapture data. The simplest version of our model used eight geographic regions (\autoref{fig:map-regions}), time-averaged movement rates, and one pooled length class. Additional versions of the model increased the resolution of the model in time (seasonal or annual time-varying movement rates) and/or introduced length length classes (small: 400--549 mm; large: 550--800 mm). Models were identified by their temporal resolution (average, season, or year) and length class (pooled or length). Sablefish movement rates correspond to per-fish transition rates between geographic regions per year, equivalent to the probability that a sablefish moved from one region to another (emigration rate) or remained within a region (retention rate) per year.

% map-regions
\begin{figure}[htb]
    \centering
    \includegraphics[width = 0.47\textwidth]{map-regions}
    \caption{Geographic sablefish regions in the northeast Pacific Ocean. Regions are Bering Sea (BS), Aleutian Islands (AI), Western (WG), Central (CG), and Eastern Gulf of Alaska (EG), Southeast Alaska (SE), British Columbia (BC), and California Current (CC). Sablefish are managed separately in Alaska (BS--EG), Southeast Alaska, British Columbia, and California Current.}
    \label{fig:map-regions}
\end{figure}

The movement model predicted annual tagged sablefish abundance in each region, and annual numbers of reported recovered tags from each release cohort. Annual survival rates were estimated from harvest, natural mortality, and tag loss rates. Reported tags were predicted using harvest rates and tag reporting rates. Movement rates, harvest rates, negative binomial dispersion, and random walk process errors (annual time-varying model only) were estimated within each model. Sablefish tag releases and recoveries were input as data. Natural mortality, tag reporting, tag loss, and initial tag loss rates were also model inputs. Stock assessment estimates were used as annual means for harvest rate priors. (See \autoref{tab:symbol-definitions}).

\subsection{Questions}
\begin{enumerate}
    \item How much do sablefish move among geographic regions? 
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:heat-region-average-pooled}
            \item Notes: standard data and priors
        \end{itemize}
    \item How sensitive are sablefish transition rates to alternative reporting rate assumptions?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:bar-sensitivity-reporting} (SI)
            \item Notes: six model fits---33\% increase or 50\% decrease for one region in each fit
        \end{itemize}
    \item How sensitive are sablefish transition rates to harvest rate priors?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: TODO scatterplot; one panel per region; retention (and CIs) vs harvest prior sd multiplier (SI)
            \item Notes: five model fits; harvest rate prior sd scaled to mean by progressively wider multiplier
        \end{itemize}    
    \item How much do sablefish transition rates vary by length class?
        \begin{itemize}
            \item Model: \texttt{region-average-length}
            \item Visual: \autoref{fig:heat-region-average-length} (SI)
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates vary by season?
        \begin{itemize}
            \item Model: \texttt{region-season-pooled}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs season  
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates vary by year?
        \begin{itemize}
            \item Model: \texttt{region-year-pooled}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs year  
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates by length class vary by season?
        \begin{itemize}
            \item Model: \texttt{region-season-length}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs season (SI)
            \item Notes: standard data and priors
        \end{itemize}
    \item How many sablefish moved between regions each year?
        \begin{itemize}
            \item Model: \texttt{region-year-length}
            \item Visual: TODO barplot; one panel per border; directional (bars) and net (line) movement
            \item Notes: standard data and priors; abundance at length data (scaled proportional to survey biomass index for Alaska regions)
        \end{itemize}    
    \item What is the relationship between sablefish density and transition rates?
        \begin{itemize}
            \item Model: \texttt{region-year-pooled}
            \item Visual: TBD
            \item Notes: TBD ideally use annual biomass estimates as proxy for relative density
        \end{itemize}    
    \item Does the movement model recover known parameters on simulated data adequately?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: TBD
            \item Notes: TBD
        \end{itemize}
\end{enumerate}

% heat-region-average-pooled
\begin{figure}[htb]
    \centering
    \includegraphics[width = 0.47\textwidth]{heat-region-average-pooled}
    \caption{Sablefish transition rates per year between geographic regions in the northeast Pacific Ocean. The main diagonal shows retention rates while the off-diagonals show emigration rates. Rows correspond to region of origin while columns represent destination. Transition rates are shown with (standard error). Regions are Regions are Bering Sea (BS), Aleutian Islands (AI), Western (WG), Central (CG), and Eastern Gulf of Alaska (EG), Southeast Alaska (SE), British Columbia (BC), and California Current (CC).}
    \label{fig:heat-region-average-pooled}
\end{figure}

\section{Supplementary Information}
% bar-sensitivity-reporting
\begin{figure}[htb]
    \centering
    \includegraphics[width = 0.7\textwidth]{bar-sensitivity-reporting}
    \caption{}
    \label{fig:bar-sensitivity-reporting}
\end{figure}

% heat-region-average-length
\begin{figure}[htb]
    \centering
    \includegraphics[width = \textwidth]{heat-region-average-length}
    \caption{Sablefish transition rates per year between geographic regions in the northeast Pacific Ocean. Left: small released length class (400--549 mm); Right: large released length class (550--800 mm). The main diagonal shows retention rates while the off-diagonals show emigration rates. Rows correspond to region of origin while columns represent destination. Transition rates are shown with (standard error). Regions are Regions are Bering Sea (BS), Aleutian Islands (AI), Western (WG), Central (CG), and Eastern Gulf of Alaska (EG), Southeast Alaska (SE), British Columbia (BC), and California Current (CC).}
    \label{fig:heat-region-average-length}
\end{figure}

\section{Tables}
% Symbol definitions
\begin{table}[ht]
  \centering
  \caption{Symbol definitions (in progress)}
  \renewcommand\arraystretch{1.2}
  \label{tab:symbol-definitions}
  \begin{tabular}{l l l l r}
    \toprule
    \textbf{Symbol} & \textbf{Condition} & \textbf{Dimension} & \textbf{Definition} & \textbf{Type} \\
    \midrule
    % Index limits
    $A$ & $\in \mathbb{Z}^{+}$ & $\in \mathbb{Z}$ & Number of geographic areas & Index limit \\
    $G_{\mathrm{rel}}$ & $\in \mathbb{Z}^{+}$ & $\in \mathbb{Z}$ & Number of release length groups & Index limit \\
    $G_{\mathrm{harv}}$ & $\in \mathbb{Z}^{+}$ & $\in \mathbb{Z}$ & Number of harvest rate length groups & Index limit \\
    $T_{\mathrm{rel}}$ & $\in \mathbb{Z}^{+}$ & $\in \mathbb{Z}$ & Number of release time steps & Index limit \\
    $T_{\mathrm{lib}}$ & $\in \mathbb{Z}^{+}$ & $\in \mathbb{Z}$ & Maximum at liberty time steps & Index limit \\
    $T_{\mathrm{study}}$ & $\in \mathbb{Z}^{+}$ & $\in \mathbb{Z}$ & Number time steps in the study & Index limit \\
    $T_{\mathrm{mov}}$ & $\in \mathbb{Z}^{+}$ & $\in \mathbb{Z}$ & Number of movement rate time steps & Index limit \\ 
    $T_{\mathrm{harv}}$ & $\in \mathbb{Z}^{+}$ & $\in \mathbb{Z}$ & Number of harvest rate time steps & Index limit \\
    $T_{\mathrm{rep}}$ & $\in \mathbb{Z}^{+}$ & $\in \mathbb{Z}$ & Number of reporting rate time steps & Index limit \\
    $T_{\mathrm{year}}$ & $\in \mathbb{Z}^{+}$ & $\in \mathbb{Z}$ & Number of release time steps per year & Index limit \\
    \midrule
    % Index functions
    $P_T \! \left(\right)$ & $\in \left[1 \, .. \, T_{\mathrm{mov}} \right]$ & $\in \mathbb{Z}$ & $P_T \colon \left[1 \, .. \, T_{\mathrm{study}} \right] \to \left[1 \, .. \, T_{\mathrm{mov}} \right]$ & Index function \\
    $H_T \! \left(\right)$ & $\in \left[1 \, .. \, T_{\mathrm{harv}} \right]$ & $\in \mathbb{Z}$ & $H_T \colon \left[1 \, .. \, T_{\mathrm{study}} \right] \to \left[1 \, .. \, T_{\mathrm{harv}} \right]$ & Index function \\
    $H_G \! \left(\right)$ & $\in \left[1 \, .. \, G_{\mathrm{harv}} \right]$ & $\in \mathbb{Z}$ & $H_G \colon \left[1 \, .. \, G_{\mathrm{rel}} \right] \to \left[1 \, .. \, G_{\mathrm{harv}} \right]$ & Index function \\
    $W_T \! \left(\right)$ & $\in \left[1 \, .. \, T_{\mathrm{rep}} \right]$ & $\in \mathbb{Z}$ & $W_T \colon \left[1 \, .. \, T_{\mathrm{study}} \right] \to \left[1 \, .. \, T_{\mathrm{rep}} \right]$ & Index function \\
    \midrule
    % Index variables
    $a_{\mathrm{rel}}$ & $\in \left[1 \, .. \, A \right]$ & $\in \mathbb{Z}$ & Release area & Index \\
    $a_{\mathrm{prev}}$ & $\in \left[1 \, .. \, A \right]$ & $\in \mathbb{Z}$ & Previous area & Index \\
    $a_{\mathrm{curr}}$ & $\in \left[1 \, .. \, A \right]$ & $\in \mathbb{Z}$ & Current area & Index \\
    $g_{\mathrm{rel}}$ & $\in \left[1 \, .. \, G_{\mathrm{rel}} \right]$ & $\in \mathbb{Z}$ & Release length group & Index \\
    $g_{\mathrm{harv}}$ & $\in \left[1 \, .. \, G_{\mathrm{harv}} \right]$ & $\in \mathbb{Z}$ & Harvest rate length group & Index \\
    $t_{\mathrm{rel}}$ & $\in \left[1 \, .. \, T_{\mathrm{rel}} \right]$ & $\in \mathbb{Z}$ & Release time step & Index \\
    $t_{\mathrm{lib}}$ & $\in \left[1 \, .. \, T_{\mathrm{lib}} \right]$ & $\in \mathbb{Z}$ & At liberty time step & Index \\
    $t_{\mathrm{curr}}$ & $\in \left[1 \, .. \, T_{\mathrm{study}} \right]$ & $\in \mathbb{Z}$ & Current time step & Index \\
    $t_{\mathrm{mov}}$ & $\in \left[1 \, .. \, T_{\mathrm{mov}} \right]$ & $\in \mathbb{Z}$ & Movement rate time step & Index \\
    $t_{\mathrm{rep}}$ & $\in \left[1 \, .. \, T_{\mathrm{rep}} \right]$ & $\in \mathbb{Z}$ & Reporting rate time step & Index \\
    \midrule
    % Input data

    % Predicted values
    % Parameters
    $\bm{p}$ & $\in \left[0, 1 \right]$ & $\in \mathbb{R}^{A \times A \times T_{\mathrm{mov}} \times G_{\mathrm{rel}}}$ & Annual movement rates between areas & Parameters \\
    $\bm{h}$ & $\in \left[0, 1 \right]$ & $\in \mathbb{R}^{G_{\mathrm{harv}} \times T_{\mathrm{harv}} \times A}$ & Annual harvest rates & Parameters \\
    $\phi$ & $\in \mathbb{R}^{+}$ & $\in \mathbb{R}$ & Negative binomial dispersion & Parameters \\
    $\bm{\sigma}$ & $\in \mathbb{R}^{+}$ & $\in \mathbb{R}^{A}$ & Optional random walk standard deviation & Parameters \\

    % $s$ & holder & Release Time & Index \\
    % $r$ & holder & Release Area & Index \\
    % $g$ & holder & Release Class & Index \\
    % $t$ & holder & Time & Index \\
    % $a$ & holder & Area & Index \\
    % $i$ & holder & Area & Index \\
    % $T_{s,r,g}$ & holder & Tags Released & Model input \\
    % $R_{s,r,g,t,a}$ & holder & Tags Recovered & Model input \\
    % $F_{t,a}$ & holder & Fishing Mortality Rate & Model input \\
    % $W_{t,a}$ & holder & Tag Reporting Rate & Model input  \\
    % $h$ & holder & Tag Loss Rate & Model input \\
    % $c$ & holder & Initial Tag Loss Rate & Model input  \\
    % $N_{s,r,g,t,a}$ & holder & Tag Abundance & Model output \\
    % $\hat{R}_{s,r,g,t,a}$ & holder & Model output Tags Recovered & Model output \\
    % $S_{t,a}$ & holder & Survival Rate & Model output \\
    % $\Phi_{i,a}$ & holder & Movement Parameters & Model output \\
    % $P_{i,a}$ & holder & Movement Rates & Model output  \\
    % $b_{g}$ & holder & Selectivity and Bias & Model output  \\
    % $M$ & holder & Natural Mortality Rate & Model output  \\
    % $\phi$ & holder & Negative Binomial Dispersion & Model output \\
    \bottomrule
  \end{tabular}
\end{table}

\newpage
\vspace{20mm}

\section{Everything below here subject to extensive revision}

\vspace{20mm}

\section{Overview}
Animal movement rates underlie spatial population dynamics and can influence the effectiveness of management strategies for harvested species. We quantified sablefish movement rates among geographic regions in the northeast Pacific by fitting Markov movement models to forty years of tag--recapture data. The simplest version of our model used three geographic regions (Alaska, British Columbia, and the US West Coast), time-averaged movement rates, and one pooled length class. Additional versions of the model increased the complexity of the model in space (subregional geographic resolution), time (seasonal or annual time-varying movement rates), or length class (small: 40--55 cm; large: 55--80 cm). Models were identified by their geographic resolution (region or subregion), temporal resolution (average, season, or annual), and length class (pooled or length). Movement rates refer to the estimated per sablefish probability of moving from one region to another (emigration rate) or remaining within a region (retention rate) per year.

The movement model predicted annual tagged sablefish abundance in each region, and annual numbers of reported tags from each release cohort. Annual survival rates were estimated from harvest, natural mortality, and tag loss rates. Reported tags were predicted using harvest rates and tag reporting rates. Movement rates, harvest rates, negative binomial dispersion, and random walk process errors (annual time-varying model only) were estimated within each model. Sablefish tag releases and recoveries were input as data. Natural mortality, tag reporting, tag loss, and initial tag loss rates were also treated as data. Stock assessment estimates were used as annual means for harvest rate priors.

\section{Questions}
% - Questions with model formulation bullets
\begin{enumerate}
    \item How much do sablefish movement rates vary between region?
    \begin{itemize}
        \item Model: \texttt{region-average-pooled}
        \item Notes: standard data and priors
        \item Visual: heat  matrix; supplemental information
    \end{itemize}
    \item How sensitive are sablefish movement rates to alternative assumptions about reporting rates?
    \begin{itemize}
        \item Model: \texttt{region-average-pooled}
        \item Notes: three model fits; 50\% increase in tag reporting rate for one region in each fit
        \item Visual: bar plot; one panel per region; retention rate vs region increased; supplemental information
    \end{itemize}
    \item How sensitive are sablefish movement rates to prior information on region specific harvest rates over time?
    \begin{itemize}
        \item Model: \texttt{region-average-pooled}
        \item Notes: five model fits with progressively wider harvest rate priors
        \item Visual: scatter plot; one panel per region; retention (and CIs) vs harvest prior sd; supplemental information
    \end{itemize}
    \item How much do sablefish movement rates vary by length class?
    \begin{itemize}
        \item Model: \texttt{region-average-length}
        \item Notes: standard data and priors
        \item Visual: heat matrix; one panel per length class; main text
    \end{itemize}
    \item How much do sablefish movement rates vary by season?
    \begin{itemize}
        \item Model: \texttt{region-season-pooled}
        \item Notes: standard data and priors
        \item Visual: scatterplot matrix; movement rate (and CIs) vs season; main text
    \end{itemize}
    \item How much do sablefish movement rates vary by year?
    \begin{itemize}
        \item Model: \texttt{region-annual-pooled}
        \item Notes: standard data and priors
        \item Visual: scatterplot matrix; movement rate (and CIs) vs year; main text
    \end{itemize}
    \item How much do sablefish movement rates vary by subregion?
    \begin{itemize}
        \item Model: \texttt{subregion-average-pooled}
        \item Notes: standard data and priors
        \item Visual: heat matrix; one panel; main text
    \end{itemize}
    \item How much do sablefish movement rates among subregions vary by year? (if possible)
    % - Brendan curious
    \begin{itemize}
        \item Model: \texttt{subregion-annual-pooled} (or \texttt{subregion-annual-length})
        \item Notes: standard data and priors
        \item Visual: scatterplot matrix; movement rate (and CIs) vs year; supplemental information
    \end{itemize}
    \item How much do sablefish movement rates by length class vary by season? (if possible)
    \begin{itemize}
        \item Model: \texttt{region-season-length} (or \texttt{subregion-season-length})
        \item Notes: standard data and priors
        \item Visual: scatterplot matrix; movement rate (and CIs) vs year; supplemental information
    \end{itemize}
    \item How many sablefish moved between regions each year?
    \begin{itemize}
        \item Model: \texttt{region-annual-length}
        \item Notes: standard data and priors
        \item Visual: barplot; one panel per border; movement north (upward) and south (downward) and net movement (line)
    \end{itemize}
\end{enumerate}

\section{Figures}
% - Somewhere show priors and posteriors (if interesting) for each estimated parameter in each model
% - Heat matrices: different colour scales for retention (dark mako) and emigration (light rocket)?
% - Spell out panel names: "small", "medium", "large", "pooled", etc.
\subsection{Main text}
\begin{enumerate}
    \item Map: northeast Pacific
    \begin{itemize}
        \item Lines (solid): Regions
        \item Lines (dashed): Subregions
        \item Points (transparent): Sablefish tag releases
    \end{itemize}
    \item Multipanel scatterplot matrix; movement rates (and CIs) vs season or year
    \begin{itemize}
        \item Column 1: \texttt{region-season-pooled}
        \item Column 2: \texttt{region-annual-pooled}
    \end{itemize}
    \item Multipanel heat matrix; movement rates (colour, text) and standard errors (text only)
    \begin{itemize}
        \item Row 1: \texttt{subregion-average-pooled} (single large panel)
        \item Row 2: \texttt{region-average-length} (panels by length class)
    \end{itemize}
    \item Barplot: net abundance exchange vs year
    \begin{itemize}
        \item Row 1: Alaska--British Columbia movement
        \item Row 2: British Columbia--US West Coast movement
        \item Bar direction: upward (north) and downward (south)
        \item Bars: Absolute movement
        \item Points and line: Net movement
        \item Superimposed on map of coast
    \end{itemize}
\end{enumerate}
\subsection{SI}
\begin{enumerate}
    \item Scatter plot: harvest rate priors and posteriors; panels by region
    \item Line plot: tag reporting rate vs year; panels by region
    \item Histogram: sablefish length distributions; length classes superimposed; panels by region
    \item Heat matrix: \texttt{region-average-pooled}
    \item Bar plot: reporting rate sensitivity
    \item Scatter plot: harvest prior sensitivity
    \item Scatter plot matrix: \texttt{subregion-annual-pooled} (if possible)
    \item Scatter plot matrix: \texttt{region-season-length} (if possible)
    \item Line plot: stock assessment abundance vs year; panels by region
    \item Barplot: net abundance exchange vs season
    \begin{itemize}
        \item Row 1: Alaska--British Columbia movement
        \item Row 2: British Columbia--US West Coast movement
        \item Bar direction: upward (north) and downward (south)
        \item Bars: Absolute movement
        \item Points and line: Net movement
    \end{itemize}

\end{enumerate}

\section{Tables}
\begin{enumerate}
    \item Summary of sablefish tag data: numbers, years, sources
    \item Movement model symbol definitions
\end{enumerate}

\newpage
\vspace{20mm}

\section{Everything below here subject to EVEN MORE extensive revision}

\vspace{20mm}

\section{MS layout}
\begin{itemize}
\item Updated versions of sections appear higher up
\item Old versions of sections appear lower down
\end{itemize}

\section{Potential co-authors}

\begin{itemize}
    \item Philina English (Figure design [x], study design [], writing/editing [ ], ...)
    \item Brendan Aulthouse % tag reporting rates
    \item Katelyn Bosley % initial model fits (Juneau)
    \item Meghan Burton % model development
    \item Sean Cox
    \item Katy Echave % tag data
    \item Daniel Goethel % study design
    \item Samuel Johnson % data inputs
    \item Lisa Lacko % tag data
    \item Chris Lunsford
    \item Andre Punt
    \item Cara Rodgveller
    \item Susan Sogard % tag data
    \item Jane Sullivan
    \item Ben Williams
\end{itemize}

% \author[3]{Brendan Aulthouse}
% \author[4]{Katelyn Bosley}
% \author[3]{Meghan Burton}
% \author[3]{Sean Cox}
% \author[6]{Katy Echave}
% \author[6]{Daniel Goethel}
% \author[3]{Samuel Johnson}
% \author[2]{Lisa Lacko}
% \author[6]{Chris Lunsford}
% \author[8]{Andre Punt}
% \author[6]{Cara Rodgveller}
% \author[9]{Susan Sogard}
% \author[10]{Jane Sullivan}
% \author[10]{Ben Williams}
% 
% \affil[2]{Pacific Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, V9T 6N7, Canada}
% \affil[3]{Resource and Environmental Management, Simon Fraser University, Burnaby, BC, V5A 1S6, Canada}
% \affil[4]{Washington Department of Fish and Wildlife, ...}
% \affil[5]{Institute of Ocean Sciences, Fisheries and Oceans Canada, Sidney, BC, V8L 5T5, Canada}
% \affil[6]{Alaska Fisheries Science Center, National Oceanic and Atmospheric Administration,
% Juneau, AK 99801, USA}
% \affil[7]{Northwest Fisheries Science Center, National Oceanic and Atmospheric Administration, Seattle, WA % 98112, USA}
% \affil[8]{School of Aquatic and Fisheries Sciences, University of Washington, Seattle WA 98105, USA}
% \affil[9]{Southwest Fisheries Science Center, National Oceanic and Atmospheric Administration, Santa Cruz, % CA 95060, USA}
% \affil[10]{National Oceanic and Atmospheric Administration, ...}

\subsection{Co-authorship criteria}
Co-authorship and final author order will be based on the PSTAT Data Sharing and Collaboration Agreement (\href{https://docs.google.com/document/d/1AXIhq6lO_qOPf7q67s_SiDOD6qEfih0COtxQZo7v-Hc/edit?usp=sharing}{here}).

@@

\noindent Keywords:

@@

\section{Methods}
% Movement modeled at end of time step

\subsection{Data}

\subsection{Model}

\subsection{Movement analyses}
% Next steps:
% - Figure script to diagnose fits (posteriors peaked relative to priors)
% - Blocked H by quarter
% - Decide separate or RW movement
% - Sensitivity to reporting rate

% Ways to reduce strain on what the model can do
% - Remove constraint on time at liberty and length buffer
% - Remove US West Coast South (which has very few large sablefish)
% - Use F from previous model fits as strong priors for subsequent
\begin{enumerate}
    \item Static ten subregion pooled
    \begin{itemize}
        \item Full time at liberty
        \item Estimate F (use as prior for length class and restricted time at liberty)
    \end{itemize}
%    \item Static ten subregion length classes
%    \begin{itemize}
%        \item Restricted time at liberty and length buffers
%        \item Use F from pooled as prior (less information to estimate it with data restrictions)
%    \end{itemize}
    \item Static three region pooled (suppress to SI)
    % Gut check on estimating F by comparison to stock assessment estimate
    \begin{itemize}
        \item Full time at liberty
        \item Estimate F (use as prior for length class and restricted time at liberty)
    \end{itemize}    
    \item Static three region length classes (suppress to SI)
    % Brendan: fitting with no constraint on liberty and buffer still worthwhile story acknowledge potential confounding in story
    \begin{itemize}
        \item Restricted time at liberty and length buffers
        \item Use F from pooled as prior (less information to estimate it with data restrictions)
    \end{itemize}
    \item Annual time-varying three region pooled
    \begin{itemize}
        \item Full time at liberty
        \item Estimate F (use as prior for length class and restricted time at liberty)
    \end{itemize} 
%    \item Annual time-varying three region length classes (if possible)
%    % Do ten subregion if everything goes smoothly, but not if poses more difficulties
%    \begin{itemize}
%        \item Restricted time at liberty and length buffers
%        \item Use F from pooled as prior (less information to estimate it with data restrictions)
%    \end{itemize}
    \item Seasonal time-varying three region pooled
    \begin{itemize}
        \item Full time at liberty
        \item Estimate F
    \end{itemize}
%   \item Seasonal time-varying three region length classes (if possible)
%   \begin{itemize}
%       \item Restricted time at liberty and length buffers
%       \item Use F from pooled as prior (less information to estimate it with data restrictions)
%   \end{itemize}
    \item Annual time-varying three region abundance exchange
    \begin{itemize}
        \item Use Annual time-varying three region length classes estimates (if possible)
        \item Use abundance estimates calculated from stock assessments
    \end{itemize}    
\end{enumerate}

\subsection{Sensitivity testing}

\subsection{Model validation}

@@

\subsection{Movement analyses}

\subsection{Sensitivity testing}

\subsection{Model validation}

@@

\section{References}

@@

\vspace{20mm}

% TODO
% See Dan Goethel's publications for notation
% Update symbols P Phi W etc in table and equations
% Check capitalization in references
% Change 'movement estimates' and 'movement probabilities' to movement rates
% Replace 'capture rate' by 'fishing mortality rate'
% Replace 'tag reporting ratio' by 'tag reporting rate'
% Specify single release single recapture
% Discuss difference--especially time step--between this and previous models
% Use 'area' in such a way as not to imply 'surface area'; consider 'geographic area'
% Include level of iteration with OM if present
% Description of F weighting equation
% Weight US West Coast catch and PC catch North / South
% Talk with Sue Sogard on WC tag reporting ratio before making a final choice
% Internal review NWFSC: Melissa; AFSC: Kari
% Justification for size classes
% AIC: static, 4 blks, 8 blks
% Time at liberty vs distance travelled cp Beamish and McFarlane
% Discussion: transboundary stock structure, recruitment patterns, spatial population dynamics
% Be sure to reference all tables and figures
% Check that all points in Abstract and Questions are addressed in Results and Discussion
% Release barplot (regions, subregions)
% Replace "reporting rate" by "index of reporting rate"
% Abundance at beginning of time step, movement at end of time step
% Sensitivity of movement rates to harvest priors
% Tags from same release caught together?
% BC: falsify resident/migrant hypothesis? Michelle Jones IBM simulation model proposal
% Simulation testing region-average-pooled
% Novelty
% - Bayesian
% - Estimating h
% - Two spatial resolutions
% - Estimating timevarying p and h

% Notes
% US Fleets are 1: HKL; 2: POT; 3: TWL

% TODO Figures
% Add land for maps
% Releases figure add recoveries panel
% Resize figures and figure components
% Three-subregion movement arrow figure like Meghan's; possibly colour by length
% Three-subregion net exchange arrow figure; movement rates one direction, net movement the other

% TODO Draft
% F for areas within EEZs
% Justification for length classes: show that small ~ immature, medium ~ maturing, large ~ mature via panel figure percent mature over age vs length
% Time-varying movement options

% Main take home messages (for abstract and restate at beginning of discussion)
% - Spatially heterogeneous movement
% - Different movement by length
% - Our estimates of PC movement away are conservative (see sensitivity)
% - Net movement into PC even though larger movement rates away from PC

% Timevarying options
% - Random effect (random walk) for movement parameters on an annual time step
% - Random effect (random walk) for movement parameters on a five or ten year time step
% - Fixed effects blocks for each decade of movement parameters

\section{Abstract}
\noindent 1. We used a Markov movement model fit to \num{\nRelTOT} tag releases and \num{\nRecTOT} tag recoveries over 40 years to estimate the movement of  sablefish among management jurisdictions (i.e, among EEZs) and at finer spatial scales in the northeast Pacific.

\noindent 2. We found that retention rates (average 93 \%) were greater than movement rates (average 7 \%) among EEZs, while retention rates (average 26 \%) were less than movement rates (average 74 \%) for areas within Alaska federal waters. Sablefish movement rates north to Alaska from Pacific Canada North (15 \%) and south to the US West Coast from Pacific Canada South (18 \%) were more than double movement rates between the two Canadian areas (average 7 \%), consistent with a hypothesized north / south separation of sablefish stocks in Pacific Canada.

\noindent 3. Time-varying movement rates were generally stable across time and length class for Alaska and the US West Coast, but varied widely for Pacific Canada where retention was lowest during 1979--1988 and 2009--2018.

\noindent 4. Despite higher per-fish movement rates out of Pacific Canada, we found that the direction of net abundance exchange was into Pacific Canada from the larger Alaska and the US West Coast populations. Movement rates between Alaska and the US West Coast were less that \num{1} \% either direction.

\noindent 5. Sablefish movement between regions may impact the success of existing management strategies, because fishing rates are set separately in different regions. Further work is needed to investigate the merits of management cooperation among regions such as a coastwide sablefish stock assessment.

\vspace{5mm}
\noindent Keywords: animal movement, movement ecology, mark-recapture, tag-recapture, time-varying movement, transboundary stock,
% release-recapture, capture-recapture

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{bm}
\usepackage{lineno}
\renewcommand\linenumberfont{\normalfont\bfseries\small\color{darkgrey}}
\usepackage{booktabs}
\usepackage[round]{natbib}
\bibliographystyle{plainnat}
\usepackage{authblk}
% Linux Libertine:
\usepackage{textcomp}
\usepackage[sb]{libertine}
\usepackage[varqu,varl]{inconsolata}% sans serif typewriter
\usepackage[libertine,bigdelims,vvarbb]{newtxmath} % bb from STIX
\usepackage[cal=boondoxo]{mathalfa} % mathcal
\useosf % osf for text, not math
\usepackage[supstfm=libertinesups,%
  supscaled=1.2,%
  raised=-.13em]{superiors}
\usepackage{setspace}
\usepackage{siunitx}
\usepackage[section]{placeins} % Keep floats (figs, tabs, eqns) in the right section
% I assume these all work together to make nice colour
\usepackage[dvipsnames]{xcolor}
\definecolor{niceblue}{HTML}{236899} % Depends \usepackage[dvipsnames]{xcolor}
\definecolor{darkgrey}{HTML}{A9A9A9} % Depends \usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=niceblue,
    citecolor=niceblue,
    linkbordercolor = white
}
% End nice colour
\usepackage{pgfplotstable} % For tables
\pgfplotsset{compat=1.16} % For tables
\input{./vals/values}
\usepackage{graphicx}
\graphicspath{ {./figs/} }

% Title
\title{}

% Authors
\author[1]{Luke A. Rogers}
\author[]{...}

%Affiliations
\affil[1]{Pacific Biological Station, Fisheries and Oceans Canada, Nanaimo, BC, V9T 6N7, Canada}

@@

\maketitle
\linenumbers
\setcounter{secnumdepth}{0}

\section{Co-authorship}
Co-authorship and final author order to folow the PSTAT Data Sharing and Collaboration Agreement (\href{https://docs.google.com/document/d/1AXIhq6lO_qOPf7q67s_SiDOD6qEfih0COtxQZo7v-Hc/edit?usp=sharing}{here}).

@@

@@

\section{Methods}

@@

@@

@@
